---
title: "insect pred"
author: "Maiga"
date: "30/10/2019"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
#packages
```{r, message=FALSE}
library(tidyverse)
library(caret)
library(ggplot2)
library(e1071)
```

# data
```{r}
insectSize = readr::read_tsv("https://raw.githubusercontent.com/shchurch/insect_egg_database_viz/master/data/dataviz_egg_database.csv")

head (insectSize)
```

# Columns selection (without logvol)
```{r}
insectSizeGroup =insectSize %>% 
  select(logX1, logX2, group)
```

# missing values

```{r}
length(which(!complete.cases(insectSizeGroup)))
```
# Proportion
```{r}
table(insectSizeGroup$group)
```
# Smaller selection of groups
```{r}
# On va garder les ordres qui sont plus nombreux (qui va simplifier le knn aussi)
insectSizeGroup_less<-insectSizeGroup[which(insectSizeGroup$group != 'Apterygota'),]
insectSizeGroup_less<-insectSizeGroup_less[which(insectSizeGroup_less$group != 'Psocodea'),]
insectSizeGroup_less<-insectSizeGroup_less[which(insectSizeGroup_less$group != 'Palaeoptera'),]
insectSizeGroup_less<-insectSizeGroup_less[which(insectSizeGroup_less$group != 'Neuropteroidea'),]
table(insectSizeGroup_less$group)
```

# No NA

```{r}
insectSizeClean <- na.omit(insectSizeGroup_less)
length(which(!complete.cases(insectSizeClean)))

#head(insectSizeClean)
```


# Normalization
```{r}
scale2 <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, TRUE)
insectSizeMeans <- insectSizeClean %>% 
                          mutate_if(is.double, scale2)
#head(insectSizeMeans)
```

# Evening out the data
```{r}
insectSizeMeans_up <- upSample(x=insectSizeMeans, y=as_factor(insectSizeMeans$group), list=FALSE)
table(insectSizeMeans_up$group)
```

# Training Set
```{r}
insectSizeTrain <- insectSizeMeans_up %>%
                  select("logX1", "logX2")


#head(insectSizeTrain)

insectSizeLabels <- insectSizeMeans_up$group
```

# Model
```{r}
k <- data.frame(k = 5)
model_knn <- train(x = data.frame(insectSizeTrain),
                   y = insectSizeLabels,
                   method='knn',
                   tuneGrid = k)
#head(model_knn)
```
# Prediction
```{r}
newObs <- data.frame(logX1= 0.577, logX2= 0.398)

predict(object = model_knn, newdata = newObs)
```

# Visualization

```{r}
new_logX1 <- seq(from = min(insectSizeTrain$logX1), to = max(insectSizeTrain$logX1), length.out = 200)
new_logX2 <- seq(from = min(insectSizeTrain$logX2), to = max(insectSizeTrain$logX2), length.out = 200)

grid_data <- expand_grid(logX1 = new_logX1,logX2 = new_logX2)

grid_data$group <- predict(object = model_knn, newdata = as.data.frame(grid_data))

insectSizeMeans %>% 
  ggplot(aes(x = logX1, y = logX2, color = group, fill = group)) + 
  geom_point(data = grid_data, alpha = 0.5)+ 
  geom_point(alpha = 0.7, pch = 21, color = "black")+ 
  scale_color_brewer(type = "qual")
  scale_fill_brewer(type = "qual")
```

# Data partition
```{r}
set.seed(500) # makes the random selection of rows reproducible
train <- insectSizeMeans_up$group %>%
          createDataPartition(p = 0.70, list = FALSE)
#head(train)

insectSizeTrain2 <- insectSizeMeans_up[train,]%>%
                        select("logX1", "logX2")
insectSizeTrainTest2 <- insectSizeMeans_up[-train,]%>%
                          select("logX1", "logX2")

insectSizeLabels2 <- insectSizeMeans_up[train,]$group
                        #select('group')

#head(insectSizeLabels2)
typeof(insectSizeLabels2)
```
# Model from partition
```{r}
k <- data.frame(k =5)
model_knn2 <- train(x = data.frame(insectSizeTrain2),
                   y = insectSizeLabels2,
                   method='knn',
                   tuneGrid = k)
#head(model_knn2)
```
#Test samples
```{r}
prediction = predict(object = model_knn2, newdata = insectSizeTrainTest2)
head(prediction)
```

#insectSizeMeans into numeric
```{r}

# Convert character vector to factor
comp = insectSizeMeans_up[-train,]$group 
        #%>%
       #select('group')
tableCompare<- factor(comp) # Laisser la fonction décider des levels pour les mettre en ordre

typeof(comp)
head(tableCompare)
```



# ConfusionMatrix

```{r}
confusionMatrix(prediction,tableCompare)
```

# Cross validation
```{r}
trainCross = trainControl(method = 'repeatedcv',
                          number = 10,
                          repeats = 1,
                          search='grid')

#tuneGrid
k <- data.frame(k =3:30)
model_knnVal <- train(x = data.frame(insectSizeTrain2),
                   y = insectSizeLabels2,
                   method='knn',
                   tuneGrid = k,
                   trControl = trainCross)

ggplot(model_knnVal, aes(x=k, y=Accuracy))+
  geom_line()
```
```{r}
head(model_knnVal)
```

# Use K=27 for training

```{r}
k <- data.frame(k =27)
model_knn3 <- train(x = data.frame(insectSizeTrain2),
                   y = insectSizeLabels2,
                   method='knn',
                   tuneGrid = k)
#head(model_knn3)
```
# Test with K=27
```{r}
prediction2 = predict(object = model_knn3, newdata = insectSizeTrainTest2)
#prediction2

```
# Confusion matrix from model K=27
```{r}
confusionMatrix(prediction2,tableCompare)
```
```{r}


new_logX1_2 <- seq(from = min(insectSizeTrain$logX1), to = max(insectSizeTrain$logX1), length.out = 200)
new_logX2_2 <- seq(from = min(insectSizeTrain$logX2), to = max(insectSizeTrain$logX2), length.out = 200)

grid_data_2 <- expand_grid(logX1 = new_logX1_2,logX2 = new_logX2_2)

grid_data_2$group <- predict(object = model_knn3, newdata = as.data.frame(grid_data_2))

insectSizeMeans %>% 
  ggplot(aes(x = logX1, y = logX2, color = group, fill = group)) + 
  geom_point(data = grid_data_2, alpha = 0.5)+ 
  geom_point(alpha = 0.7, pch = 21, color = "black")+ 
  scale_color_brewer(type = "qual")
  scale_fill_brewer(type = "qual")

```

